Computer Science House Constitution

### 2024-02-20 constitution.tex
Reword 5.D.1.B.1 since it was really long and repeated a lot of the same information. (#144)
* mmmmmmmmmm member dues are yummy why cant we eat them?

* Add language to explicitly allow for reduction and extension

---------

Co-authored-by: Sam Cordry <samcordry@gmail.com>
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>

\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to E-Board.
If E-Board disagrees with the Financial Director, E-Board may reduce the required payment or extend the payment deadline.
If E-Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or E-Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual Membership Evals (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.

>>>>

\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay requested dues, they may appeal their situation to the Financial Director.
The Financial Director then decides whether their situation warrants an extension to the payment deadline and/or reduction of the required dues.
If the Financial Director decides their situation warrants no action, the member may appeal this decision to E-Board.
If appealed, E-Board may provide an extension and/or reduction to the member.
If the appeal is denied, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
